---
title: "nhanes"
format: html
editor: visual
---

Load libraries

```{r Dependencies}
#| echo: false
library(foreign)
library(tidyverse)
library(purrr)
library(svyVGAM)
```

Loading NHANES data and save as a R data file. A separate dataframe with column names is also saved separately. Helps to search variables easily.

For NHANES data, handling need to be done calculating the survey weights.

```{r 1999-2000}
#| echo: false
#read file directly from the url of NHANES

#df for 1999-2000 
abpi_9900<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/LEXABPI.XPT"))
alliron_9900<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/LAB06.XPT"))
diab_9900<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/DIQ.XPT"))
demo_9900<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/DEMO.XPT"))
ldl_tg_9900<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/LAB13AM.XPT"))
hdl_total_9900<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/LAB13.XPT"))
crp_9900<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/LAB11.XPT"))
gluc_ins_9900<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/LAB10AM.XPT"))
otherlab_9900<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/LAB18.XPT"))
ht_9900<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/BPQ.XPT"))
smoking_9900<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/SMQ.XPT"))
bmi_9900<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/BMX.XPT"))
hemo_9900<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/LAB25.XPT"))
preg_9900<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/SEQ.XPT"))
medcon_9900<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/MCQ.XPT"))
alc_9900<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/ALQ.XPT"))
hba1c_9900<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/LAB10.XPT"))
paq_9900<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/PAQIAF.XPT"))
paq2_9900<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/PAQ.XPT"))
bld.don_9900<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/HSQ.XPT"))
rep.health_9900<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/RHQ.XPT"))
oral.health_9900<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/OHXREF.XPT"))
urine_9900<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/LAB16.XPT"))
#0912 is the drug code for antihyperlipidemics in 99-00
#to pickup antiplatelet, use name detection
pattern <- paste(c("ASPIRIN", "CLOPIDOGREL", "TICLOPIDINE","DIPYRIDAMOLE"), collapse = "|")
medicine_9900<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/RXQ_RX.XPT"))%>%
  select(SEQN,RXD240B,FDACODE1,FDACODE2,FDACODE3,FDACODE4,FDACODE5,FDACODE6)%>%
  mutate(antihy.lipid=rowSums(across(.cols = everything(), ~str_detect(.x, fixed("0912")))),
         anti.platelet=if_else(str_detect(RXD240B,regex(pattern)),1,0))%>%
  select(SEQN,antihy.lipid,anti.platelet)%>%
  unique()
rm(pattern)
bp_9900<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/BPX.XPT"))

#merge all dataframes and save as reference data file
df9900<-purrr::reduce(list(alliron_9900,diab_9900,demo_9900,
                               ldl_tg_9900,hdl_total_9900,
                               crp_9900,gluc_ins_9900,otherlab_9900,ht_9900,smoking_9900,bmi_9900,hemo_9900,preg_9900,medcon_9900,alc_9900,hba1c_9900,paq_9900,paq2_9900,
                           bld.don_9900,rep.health_9900,oral.health_9900,urine_9900,medicine_9900,bp_9900),
                          dplyr::full_join, by = 'SEQN')%>%
  right_join(abpi_9900,by = 'SEQN')%>%
  mutate(MEC6YR=2/3 * WTMEC4YR)#calculate survey weight
  
#as_survey_design(weights = MEC6YR,ids = SDMVPSU)%>%
#  summarise(mean_age=survey_mean(RIDAGEYR,vartype=NULL))


#save a single object to a file
saveRDS(df9900, "~/Docs/myRprojects/nhanes/data_files/df9900.rds")


#save colnames and attributes as a separate dataframe
#df9900_names<-purrr::map_df(df9900, ~attributes(.x)) %>%
#  bind_cols(names = names(df9900), .)
#saveRDS(df9900_names, "~/Docs/myRprojects/nhanes/data_files/df9900_names.rds")


```

```{r NHANES 2001-2002}
#read file directly from the url of NHANES

#df for 2001-2002 
abpi_0102<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/LEXAB_B.XPT"))
ferritin_0102<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/L06_2_B.XPT"))
otheriron_0102<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/L40FE_B.XPT"))
diab_0102<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/DIQ_B.XPT"))
demo_0102<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/DEMO_B.XPT"))
ldl_tg_0102<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/L13AM_B.XPT"))
hdl_total_0102<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/L13_B.XPT"))
crp_0102<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/L11_2_B.XPT"))
gluc_ins_0102<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/L10_2_B.XPT"))
otherlab_0102<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/L40_B.XPT"))
ht_0102<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/BPQ_B.XPT"))
smoking_0102<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/SMQ_B.XPT"))
bmi_0102<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/BMX_B.XPT"))
hemo_0102<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/L25_B.XPT"))
preg_0102<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/RHQ_B.XPT"))
medcon_0102<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/MCQ_B.XPT"))
alc_0102<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/ALQ_B.XPT"))
hba1c_0102<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/L10_B.XPT"))
paq_0102<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/PAQIAF_B.XPT"))
paq2_0102<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/PAQ_B.XPT"))
bld.don_0102<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/HSQ_B.XPT"))
oral.health_0102<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/OHXREF_B.XPT"))
urine_0102<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/L16_B.XPT"))
pattern <- paste(c("ASPIRIN", "CLOPIDOGREL", "TICLOPIDINE","DIPYRIDAMOLE"), collapse = "|")
medicine_0102<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/RXQ_RX_B.XPT"))%>%
  select(SEQN,RXD240B,FDACODE1,FDACODE2,FDACODE3,FDACODE4,FDACODE5,FDACODE6)%>%
  mutate(antihy.lipid=rowSums(across(.cols = everything(), ~str_detect(.x, fixed("0912")))),
         anti.platelet=if_else(str_detect(RXD240B,regex(pattern)),1,0))%>%
  select(SEQN,antihy.lipid,anti.platelet)%>%
  unique()
rm(pattern)
bp_0102<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2001-2002/BPX_B.XPT"))
#merge all dataframes and save as reference data file
df0102<-purrr::reduce(list(ferritin_0102,otheriron_0102,diab_0102,demo_0102,
                               ldl_tg_0102,hdl_total_0102,
                               crp_0102,gluc_ins_0102,otherlab_0102,ht_0102,smoking_0102,
                           bmi_0102,hemo_0102,preg_0102,medcon_0102,alc_0102,hba1c_0102,
                           paq_0102,paq2_0102,
                           bld.don_0102,oral.health_0102,urine_0102,medicine_0102,bp_0102),
                          dplyr::full_join, by = 'SEQN')%>%
  right_join(abpi_0102,by = 'SEQN')%>%
  mutate(MEC6YR=2/3 * WTMEC4YR)#calculate survey weight

#save a single object to a file
saveRDS(df0102, "~/Docs/myRprojects/nhanes/data_files/df0102.rds")

#some labels of the 01-02 dataset are missing so they need to be added
library(labelled)
var_label(df0102)<-list(LB2BCDSI="Cadmium (nmol/L)",LB2BPBSI="Lead (umol/L)",
                        LB2RBFSI="Folate, RBC (nmol/L RBC)",LB2THGSI="Mercury, total (umol/L)",
                        LB2HCY="Homocysteine(umol/L)",LB2FERSI="Ferritin (ug/L)",
                        LB2B12SI="Vitamin B12, serum (pmol/L)",LB2FOLSI="Folate, serum (nmol/L)",
                        LB2COTLC="Cotinine comment code"
                        )

#save colnames and attributes as a separate dataframe
#df0102_names<-purrr::map_df(df0102, ~attributes(.x)) %>%
#  bind_cols(names = names(df0102), .)
#saveRDS(df0102_names, "~/Docs/myRprojects/nhanes/data_files/df0102_names.rds")
```

```{r NHANES_2003-2004}
#read file directly from the url of NHANES

#df for 2003-2004 
abpi_0304<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/LEXAB_C.XPT"))
ferritin_tfr_0304<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/L06TFR_C.XPT"))
otheriron_0304<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/L40FE_C.XPT"))
diab_0304<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/DIQ_C.XPT"))
demo_0304<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/DEMO_C.XPT"))
ldl_tg_0304<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/L13AM_C.XPT"))
hdl_total_0304<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/L13_C.XPT"))
crp_0304<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/L11_C.XPT"))
gluc_ins_0304<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/L10AM_C.XPT"))
otherlab_0304<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/L40_C.XPT"))
ht_0304<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/BPQ_C.XPT"))
smoking_0304<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/SMQ_C.XPT"))
bmi_0304<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/BMX_C.XPT"))
hemo_0304<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/L25_C.XPT"))
preg_0304<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/RHQ_C.XPT"))
medcon_0304<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/MCQ_C.XPT"))
alc_0304<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/ALQ_C.XPT"))
hba1c_0304<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/L10_C.XPT"))
paq_0304<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/PAQIAF_C.XPT"))
paq2_0304<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/PAQ_C.XPT"))
bld.don_0304<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/HSQ_C.XPT"))
oral.health_0304<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/OHXREF_C.XPT"))
urine_0304<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/L16_C.XPT"))

#joining medicine for 03-04 involves combining drug information with drug codes and then detecting patterns
medinfo_0304<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/1999-2000/RXQ_DRUG.xpt"))
medicine_0304<- haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/RXQ_RX_C.XPT"))%>%
  left_join(medinfo_0304,by="RXDDRGID")%>%
  select(SEQN,RXDDCN1B,RXDDCN1C,RXDDCN2B)%>%
  mutate(antihy.lipid=rowSums(across(.cols = everything(), ~str_detect(.x, "HYPERLIPIDEMIC"))),
         antihy.lipid=recode(antihy.lipid,"2"=1),
         anti.platelet=rowSums(across(.cols = everything(), ~str_detect(.x, "ANTIPLATELET"))))%>%
  select(SEQN,antihy.lipid,anti.platelet)%>%
  unique()
rm(medinfo_0304)
urine_0304<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/L16_C.XPT"))
bp_0304<-haven::read_xpt(url("https://wwwn.cdc.gov/Nchs/Nhanes/2003-2004/BPX_C.XPT"))

#merge all dataframes and save as reference data file
df0304<-purrr::reduce(list(ferritin_tfr_0304,otheriron_0304,diab_0304,demo_0304,
                               ldl_tg_0304,hdl_total_0304,
                               crp_0304,gluc_ins_0304,otherlab_0304,ht_0304,smoking_0304,bmi_0304,hemo_0304,preg_0304,medcon_0304,alc_0304,hba1c_0304,paq_0304,paq2_0304,
                           bld.don_0304,oral.health_0304,urine_0304,medicine_0304,bp_0304),
                          dplyr::full_join, by = 'SEQN')%>%
  right_join(abpi_0304,by = 'SEQN')%>%
  mutate(MEC6YR=1/3 * WTMEC2YR)#calculate survey weight

#save a single object to a file
saveRDS(df0304, "~/Docs/myRprojects/nhanes/data_files/df0304.rds")

#save colnames and attributes as a separate dataframe
#df0304_names<-purrr::map_df(df0304, ~attributes(.x)) %>%
#  bind_cols(names = names(df0304), .)
#saveRDS(df0304_names, "~/Docs/myRprojects/nhanes/data_files/df0304_names.rds")
```

For analysis, load the datafiles and select the variables of interest: albumin, AST, ALT, BUN, T.Chol, Iron, TGs, Creat, FPG, Insulin, Ferritin, TIBC, HDL, LDL, Gender, Age, Diabetes, Left ABPI, Right ABPI, TSAT, Smoking now, number of cigarettes, HT, CRP,BMI, hemoglobin, BP,ethnicity, insulin inj, oral antidiabetic medication,pregnant, anemia treatment,alcohol intake, hba1c,anti-ht medication,cancer,drinks_perday, leisure activity, activity level, MET activity,vig activity in 30 days, moderate activity in 30 days, last blood donation,periods now,estrogen pills now,progesterone pills now,estrogen/progesterone pills now,estrogen patch now, estrogen/progesterone patch now, breast feeding now,psu,strata,platelet count,dialysis,albuminuria,creatininuria,pregnant_lastyr,antihyperlipidemic, antiplatelet, systolic bp, diastolic bp.

Note: the variable codes could be different for the NHANES datasets of other years

```{r NHANES_2003-2004_Selected-variables}


df9900_sel<-readRDS("~/Docs/myRprojects/nhanes/data_files/df9900.rds")%>%
  dplyr::select(SEQN,LBDSALSI,LBXSATSI,LBXSASSI,LBDSBUSI,LBDSCHSI,
                LBDIRNSI,LBDSTRSI, LBDSCRSI,LBXGLUSI,LBXINSI,
                LBDFERSI,LBDTIBSI,LBDHDLSI,LBDLDLSI,
                RIAGENDR,RIDAGEYR,DIQ010,LEXLABPI,LEXRABPI,
                LBXPCT,SMQ040,SMQ020,BPQ030,LBXCRP,BMXBMI,LBXHGB,SDMVPSU,MEC6YR,RIDRETH2,DIQ050,DIQ070,SEQ060,MCQ053,ALQ110,LBXGH,BPQ040A,MCQ220,PADTIMES,PADMETS,PAD200,PAD320,HSQ570,RHQ050,RHQ558,RHQ566,RHQ574,RHQ584,RHQ600,RHQ200,SDMVSTRA,LBXPLTSI,OHQ144,URXUMASI,URXUCRSI,RHQ040,antihy.lipid,anti.platelet,BPXSAR,BPXDAR)%>%unique()

df0102_sel<-readRDS("~/Docs/myRprojects/nhanes/data_files/df0102.rds")%>%
  dplyr::select(SEQN,LBDSALSI,LBXSATSI,LBXSASSI,LBDSBUSI,LBDSCHSI,
                LBDIRNSI,LBDSTRSI, LBDSCRSI,LB2GLUSI,LB2INSI,
                LB2FERSI,LBDTIBSI,LBDHDLSI,LBDLDLSI,
                RIAGENDR,RIDAGEYR,DIQ010,LEXLABPI,LEXRABPI,
                LBDPCT,SMQ040,SMQ020,BPQ030,LB2CRP,BMXBMI,LBXHGB,SDMVPSU,MEC6YR,RIDRETH2,
                DIQ050,DIQ070,RHQ141,MCQ053,ALQ110,LBXGH,BPQ040A,MCQ220,PADTIMES,PADMETS,PAD200,PAD320,HSD570,RHQ050,RHQ558,RHQ566,RHQ574,RHQ584,RHQ600,RHQ200,SDMVSTRA,LBXPLTSI,OHQ144,URXUMASI,URXUCRSI,RHQ040,antihy.lipid,anti.platelet,BPXSAR,BPXDAR)%>%unique()

df0304_sel<-readRDS("~/Docs/myRprojects/nhanes/data_files/df0304.rds")%>%
  dplyr::select(SEQN,LBDSALSI,LBXSATSI,LBXSASSI,LBDSBUSI,LBDSCHSI,
                LBDIRNSI,LBDSTRSI, LBDSCRSI,LBDGLUSI,LBDINSI,
                LBDFERSI,LBDTIBSI,LBDHDDSI,LBDLDLSI,
                RIAGENDR,RIDAGEYR,DIQ010,LEXLABPI,LEXRABPI,
                LBDPCT,SMQ040,SMQ020,BPQ030,LBXCRP,BMXBMI,
                LBXHGB,SDMVPSU,MEC6YR,RIDRETH2,
                DIQ050,DIQ070,RHD143,MCQ053,ALQ110,LBXGH,BPQ040A,MCQ220,PADTIMES,PADMETS,PAD200,PAD320,HSQ571,RHQ051,RHQ558,RHQ566,RHQ574,RHQ584,RHQ600,RHQ200,SDMVSTRA,LBXPLTSI,OHQ144,URXUMASI,URXUCRSI,RHD042,antihy.lipid,anti.platelet,BPXSAR,BPXDAR)%>%unique()

```

Rename variables to enable appending of datasets

```{r Rename}
names<-c(seqn=1,albumin=2, ast=3, alt=4, urea=5, t.chol=6, iron=7,
tg=8, creatinine=9, fpg=10, insulin=11, ferritin=12, tibc=13, hdl=14,
ldl=15, gender=16, age=17, diabetes=18, left.abpi=19, right.abpi=20, 
tsat=21, smoke_now=22, smoked_100=23,ht=24,crp=25,bmi=26,hb=27,
psu=28,persWeight=29,ethnicity=30,insulin_now=31,antidiab_now=32,
pregnant_now=33,iron_suppl=34,drinks_life=35,hba1c=36,antiht_now=37,
cancer=38,pa.times=39,met.score=40,vig.activity=41,
mod.activity=42,last_bld.don=43,periods_now=44,est.pills_now=45,prog.pills_now=46,estprog.pills_now=47,est.patches_now=48,estprog.patches_now=49,breast.feed_now=50,strata=51,platelet=52,dialysis=53,albuminuria=54,creatinuria=55,periods_1yr=56,sbp=59,dbp=60)

df9900_sel<-df9900_sel%>%
  dplyr::rename(names)%>%
  mutate(study="nhanes99-00")

df0102_sel<-df0102_sel%>%
  dplyr::rename(names)%>%
  mutate(study="nhanes01-02")

df0304_sel<-df0304_sel%>%
  dplyr::rename(names)%>%
  mutate(study="nhanes03-04")


#save a single object to a file
saveRDS(df9900_sel, "~/Docs/myRprojects/nhanes/data_files/df9900_sel.rds")
saveRDS(df0102_sel, "~/Docs/myRprojects/nhanes/data_files/df0102_sel.rds")
saveRDS(df0304_sel, "~/Docs/myRprojects/nhanes/data_files/df0304_sel.rds")

#append all datasets to one for analysis
df_all<-dplyr::bind_rows(df9900_sel,df0102_sel,df0304_sel)%>%
  unique()

#save a single object to a file
saveRDS(df_all, "~/Docs/myRprojects/nhanes/data_files/df_all.rds")

#remove unwanted files
rm(df0102_sel,df9900_sel,df0304_sel)
rm(alliron_9900,diab_9900,demo_9900,
                               ldl_tg_9900,hdl_total_9900,
                               crp_9900,gluc_ins_9900,otherlab_9900,ht_9900,smoking_9900,
   bmi_9900,hemo_9900,preg_9900,medcon_9900,alc_9900,hba1c_9900,paq_9900,paq2_9900,
                           bld.don_9900,rep.health_9900,oral.health_9900,urine_9900,
   df9900_names,medicine_9900,bp_9900)
rm(ferritin_0102,otheriron_0102,diab_0102,demo_0102,
                               ldl_tg_0102,hdl_total_0102,
                               crp_0102,gluc_ins_0102,otherlab_0102,ht_0102,smoking_0102,
                           bmi_0102,hemo_0102,preg_0102,medcon_0102,alc_0102,hba1c_0102,
                           paq_0102,paq2_0102,
                           bld.don_0102,oral.health_0102,urine_0102,df0102_names,medicine_0102,bp_0102)
rm(ferritin_tfr_0304,otheriron_0304,diab_0304,demo_0304,
                               ldl_tg_0304,hdl_total_0304,
                               crp_0304,gluc_ins_0304,otherlab_0304,ht_0304,smoking_0304,bmi_0304,hemo_0304,preg_0304,medcon_0304,alc_0304,hba1c_0304,paq_0304,paq2_0304,
                           bld.don_0304,oral.health_0304,urine_0304,df0304_names)
rm(df9900,df0102,df0304,abpi_9900,abpi_0102,abpi_0304,medicine_0304,bp_0304)
```
